---
title: "Intro to basics"
description: In this chapter, you will take your first steps with R. You will learn
  how to use the console as a calculator and how to assign variables. You will also
  get to know the basic data types in R. Let's get started!
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Arithmetic with R

In its most basic form, R can be used as a simple calculator. Consider the following arithmetic operators:

- Addition: `+`
- Subtraction: `-`
- Multiplication: `*`
- Division: `/`
- Exponentiation: `^`
- Modulo: `%%`

## Arithmetic with R

The last two might need some explaining:

- The `^` operator raises the number to its left to the power of the number to its right: for example `3^2` is `9`.
- The modulo returns the remainder of the division of the number to the left by the number on its right, for example 5 modulo 3 or `5 %% 3` is 2.

With this knowledge, follow the instructions below to complete the exercise.

## Arithmetic with R
- Type `2^5` in the editor to calculate 2 to the power 5.
```{r}
2^5
```
- Type `28 %% 6` to calculate 28 modulo 6.
```{r}
28 %% 6
```

- Note how the `#` symbol is used to add comments on the R code.

```{r, echo=TRUE}
# Another example of the modulo operator: `9 %% 2` equals `1`.
9 %% 2
```


